OpenMPIR

### 2017-09-09 paper.tex
Fixed weird typos in omp pragmas in text

@@

For this work we replaced a subset of the OpenMP implementation to generate
Tapir IR instead of vanilla LLVM IR with OpenMP runtime calls. Specifically, we
replace the two primary \texttt{task\_spawn} and
\texttt{task\_wait} pragmas for task parallelism. By re-using code from Schardl et al.\ for code generation
of Cilk constructs, we were able to easily generate Tapir code for these OpenMP
pragmas. The ease with which this was completed is a testament to the quality of
the Tapir implementation.

While we did implement the codegen for the \texttt{task\_spawn} and
\texttt{task\_wait} constructs, it's worth noting that even for these
pragmas the implementation is incomplete. Currently, any clauses modifying the
behavior of the pragmas is ignored. Probably the most common semantics this
will change is for the semantcis of variables, e.g.\ \texttt{shared} vs.\ \texttt{private}.
Surprisingly, this had little effect on the correctness of the entire Barcelona
OpenMP task suite. Indeed, it is likely that fixing this problem would marginally increase
performance by reducing the number of memory
copies for variables declared \texttt{private} in OpenMP code.  The fact
that behaviour wasn't changed significantly is worth revisiting, and we do so
in Section~\ref{Sec:Discussion}.

@@

Thanks to Kei Davis for his excellent editing.

>>>>

\author{Kei Davis}
\affiliation{\institution{Los Alamos National Laboratory}}
\email{kei@lanl.gov}

@@

For this work we replaced a subset of the OpenMP implementation to generate
Tapir IR instead of vanilla LLVM IR with OpenMP runtime calls. Specifically, we
replace the two primary \texttt{task} and \texttt{taskwait} pragmas for task
parallelism. By re-using code from Schardl et al.\ for code generation of Cilk
constructs, we were able to easily generate Tapir code for these OpenMP
pragmas. The ease with which this was completed is a testament to the quality
of the Tapir implementation.

While we did implement the codegen for the \texttt{task} and
\texttt{taskwait} constructs, it's worth noting that even for these pragmas
the implementation is incomplete. Currently, any clauses modifying the behavior
of the pragmas is ignored. Probably the most common semantics this will change
is for the semantcis of variables, e.g.\ \texttt{shared} vs.\ \texttt{private}.
Surprisingly, this had little effect on the correctness of the entire Barcelona
OpenMP task suite. Indeed, it is likely that fixing this problem would
marginally increase performance by reducing the number of memory copies for
variables declared \texttt{private} in OpenMP code.  The fact that behaviour
wasn't changed significantly is worth revisiting, and we do so in
Section~\ref{Sec:Discussion}.

@@
